Embedding Intuitionistic into Classical Logic

### 2023-03-06 FoSSaCS/rebuttal.txt

Thank you for your insightful reviews. We will take the feedback into account for preparing the final version. We now address the points raised by the reviewers:

R1, "erroneous translations":

We agree that the translation is incomplete as given. However, this issue is a minor mistake in the write-up and can be easily be fixed (moreover, our implementation already handles the observed issue correctly): That the translation is incomplete is due to the fact that definition 9 handles universally quantified variables differently than free variables (which are not translated at all). This incompleteness arises from the fact that the translation is only intended to be used on sentences. However, the inductive nature of definition 9 necessitates that φᶜ be defined even when not all variables are quantified. With this in mind we can easily fix the problem by changing definition 9 analogously to definition 5, i.e. replacing all free variables with bound ones and universally quantifying over them before applying the transformation. We note that our tool already introduces the necessary universal quantifiers during the normalization, and so is not affected by the observed issue. We further note that the results of our tool are validated against the known results of the ILTP set, which increases the confidence in the correctness of our translation (and indeed allowed us to fix bugs during implementation).

R1, "lack of clarity and rigour":

We believe that the level of technical detail of our paper is on par with related papers from the literature. We judged that, besides taking up precious space, the inclusion/repetition of standard definitions would occlude the contributions of our paper. Such omissions are quite usual, even in papers where syntax is relevant, e.g. [1, 2, 3]. In particular notions such as atomic formulas or ground expressions are rarely ever defined.  While our definitions of semantics suggest the underlying languages we concede that they should be made explicit.

 [1] Otten, Jens. "Clausal connection-based theorem proving in intuitionistic first-order logic." International Conference on Automated Reasoning with Analytic Tableaux and Related Methods. Springer, Berlin, Heidelberg, 2005.

 [2] Parigot, Michel. "λμ-calculus: an algorithmic interpretation of classical natural deduction." International Conference on Logic for Programming Artificial Intelligence and Reasoning. Springer, Berlin, Heidelberg, 1992.

 [3] Baaz, Matthias and Iemhoff, Rosalie. "The Skolemization of existential quantifiers in intuitionistic logic." Annals of Pure and Applied Logic 142.1-3 (2006): 269-295.

We are thankful for the points raised by the reviewer and we will do our best to integrate them, which will improve the quality of our paper.

We address a few selected points by the reviewer:

- We agree that a definition of the formal languages should be noted and we will give either an exact definition or reference.

- As correctly observed, the paper was written with distinct sets of free and bound variables in mind, with letters a, b usually indicating free variables and u, w, x, y bound ones (see e.g. definition 5). We agree that the distinction between free and bound variables should be noted.

- We cannot fully understand the criticism of Definition 7:
 * Cᴵ(m) is true iff m ∈ Cᴵ, similarly Aᴵ(m) → Bᴵ(m) is false iff m ∈ Aᴵ and not m ∈ Bᴵ. While one could be more deliberate in their terminology, this is not so unusual.
 * The notation [ψ] was introduced precisely so that f^I_{[ψ]} would be defined for ψ ∈ X, since f_ψ is only defined for ψ ∈ X^{uS} in Lemma 6.
 * s is also introduced in Lemma 6.
 * Definition 7 defines for every counter-model M of ψ^{CH} a modified model M_T. Corollary 1 is in line with this.

- We will incorporate the suggestions by the reviewer to improve clarity, e.g. requiring certain sets to be finite.

R2, "use of QBF solvers for the propositional case": We agree that it would be interesting to test the performance of our translation for the propositional case. However the interest in intuitionistic propositional logic is lower than for the first-order case, where applications are more evident, e.g. program extraction. Therefore we focused our evaluation efforts on the first-order case.

R3, "However, it isn't clear whether these adjustments would indeed close the gap.": Indeed, the results do not demonstrate that our approach has the potential to outperform other algorithms on the general problem. However, there is sufficient evidence that on certain subsets it can, namely at the very least for |Q| = 0 and |X| < 3 (referring to Fig. 3). Note in particular that our tool is quite efficient in applying a classical solver if |Q| = |X| = 0. It could be useful as part of a portfolio solver even at this point.

### 2023-03-06 LPAR/LPAR-EIICL.tex
LPAR

\documentclass[runningheads]{llncs}
\usepackage{amsmath, amsfonts}
\usepackage{wrapfig}
\usepackage{multicol}
\usepackage[T1]{fontenc}
\usepackage{todonotes}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%
\usepackage{tikz}
\usetikzlibrary{shapes,backgrounds}

\begin{document}
	%
	\title{Embedding Intuitionistic into Classical Logic}
	%
	%\titlerunning{Abbreviated paper title}
	% If the paper title is too long for the running head, you can set
	% an abbreviated paper title here
	%
	\author{Alexander Pluska \and Florian Zuleger}
	%
	\authorrunning{A. Pluska and F. Zuleger}
	% First names are abbreviated in the running head.
	% If there are more than two authors, 'et al.' is used.
	%
	\institute{TU Wien, Vienna, Austria}
	%
	\maketitle
\begin{abstract}
The famous double negation translation~\cite{glivenko1929quelques,godel1933intuitionistischen} establishes an embedding of classical into intuitionistic logic.
Curiously, the reverse direction has not been covered in literature.
Utilizing a normal form for intuitionistic logic~\cite{claessen2015sat}, we establish a small model property for intuitionistic propositional logic.
We use this property for a direct encoding of the Kripke semantics into classical propositional logic and quantified boolean formulas.
Next, we transfer the developed techniques to the first order case and provide an embedding of intuitionistic first-order logic into classical first-order-logic.
Our goal here is an encoding that facilitates the use of state-of-the-art provers for classical first-order logic for determining intuitionistic validity.
In an experimental evaluation, we show that our approach can compete with state-of-the-art provers for certain classes of benchmarks, in particular when the intuitionistic content is low.
We further note that our constructions support the transfer of counter-models to validity, which is a desired feature in model checking applications.
\end{abstract}

@@

Constructive mathematics refers to a flavour of mathematics in which the existence of an object can only be established by explicit construction, as opposed to classical mathematics where existence can be shown implicitly, e.g. by assuming non-existence and deriving a contradiction.
The formalism usually associated with constructive mathematics is intuitionistic logic, which essentially differentiates itself from classical logic by the fact that the law of excluded middle $A\vee\neg A$ and the double negation shift $\forall x\neg\neg P(x)\to\neg\neg\forall xP(x)$ are not valid.
Besides philosophical considerations, most prominently advocated by Brouwer~\cite{brouwer1907over} and Bishop~\cite{bishop1967foundations}, there is a particular motivation for studying constructive mathematics from the perspective of computer science in that proofs in intuitionistic logic directly correspond to computer programs --- as expressed in the Curry--Howard correspondence~\cite{howard1980formulae}.

The interest in intuitionistic logic has lead to the development of a number of automated theorem proving systems and a collection of benchmark problems (see e.g. the ILTP library website~\cite{iltp}).
The progress in automated reasoning for intuitionistic logic, however, has been slower than the  impressive advances in solvers for classic logics --- evidenced, e.g., by the CASC~\cite{casc} and SAT~\cite{satc} competitions.
%, e.g., the first-order provers~\cite{kovacs2013first, schulz2002brainiac, korovin2008iprover}
%Comparing benchmarks for classical and intuitionistic automated theorem proving, e.g. TPTP~\cite{casc} and , we see that classical provers currently have a far better success rate. Furthermore all the most popular first-order utilize classical logic.
This difference can partially be explained by fundamental differences between the logics.
First of all, determining intuitionistic validity is computationally harder, e.g., in the propositional case intuitionistic validity is \verb+PSPACE+-complete~\cite{statman1979intuitionistic}, whereas classical validity is \verb+coNP+-complete~\cite{cook1971complexity}.
A further advantage of classical logic is the existence of calculi that are particularly suited for automation, such as superposition~\cite{bachmair2001resolution}, which rely on the existence of convenient normal forms such as CNF, and the duality between validity and satisfiability (i.e., in order to show the validity of a formula it suffices to show the unsatisfiability of the negated formula, which is insufficient in intuitionistic logic).
The first dedicated intuitionistic theorem provers~\cite{mclaughlin2009efficient,tammet1996resolution} used the naive inverse method, i.e., a direct search for a cut-free proof by applying the rules from some proof calculus inversely, which generally leads to a very complex search. 
More recently, connection-based methods have been applied to various non-classical logics~\cite{otten2005clausal,otten2021nanocop}, including intuitionistic logic.
There have also been some successful attempts to study intuitionistic validity via embedding into higher-order classical logic~\cite{LEO}.
We finally add that, in contrast to intuitionistic provers, a tremendous amount of work has been put into optimizing provers for classical logic.

@@

In this section we fix notation and recall the semantics for classical and intuitionistic logic. Futhermore we recapitulate some results from~\cite{otten2005clausal}.

@@

\begin{definition}
	Let $\Sigma$ be a signature. A $\Sigma$-structure $\mathcal{M}$ consists of a non-empty set $M$, the \emph{domain} of $\mathcal{M}$, and an \emph{interpretation} $I$ that assigns
	\begin{itemize}
		\item to each $n$-ary function symbol $f\in\Sigma$ a $n$-ary function $f^I: M^n\to M$.
		\item to each $n$-ary relation symbol $R\in\Sigma$ a $n$-ary relation $R^I\subseteq M^n$.
	\end{itemize}
	A variable assignment $v$ is a function that assigns to each free variable an element $m\in M$. For each free variable $a$ and $m\in M$ we define $$v[m/a](b) = \begin{cases}
	m, &\text{if $b=a$,}\\
	v(b), &\text{otherwise.}
	\end{cases}$$
	Then terms are interpreted as follows:
	\begin{itemize}
		\item $a^{I, v} = v(a)$ for each free variable $a$.
		\item $f(t_1,\dots,t_n)^{I, v} = f^I(t_1^{I, v},\dots, t_n^{I, v})$ for each $n$-ary function symbol $f\in\Sigma$.
	\end{itemize}
	We define a model relation between pairs $\mathcal M, v$ and formulas $\varphi$ as follows
	\begin{itemize}
		\item $\mathcal M, v\not\models\bot$
		\item $\mathcal M, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I, v},\dots,t_n^{I, v})\in R^I$, $\mathcal M, v\models s = t$ iff $s^{I, v} = t^{I, v}$.
		\item $\mathcal M, v\models \varphi\wedge \psi$ iff $\mathcal M, v\models\varphi$ and $\mathcal M, v\models\psi$
		\item $\mathcal M, v\models \varphi\vee\psi$ iff $\mathcal M, v\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\to\psi$ iff $\mathcal M, v\not\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models\exists x\varphi$ iff there exists $m\in M$ such that $\mathcal M, v[m/a]\models\varphi[a/x]$.
		\item $\mathcal M, v\models\forall x\varphi$ iff for all $m\in M$ we have $\mathcal M, v[m/a]\models\varphi[a/x]$.
	\end{itemize}
	 Here $a$ is a free variable that does not occur in $\varphi$. A $\Sigma$-structure $\mathcal M$ satisfies $\varphi$ if $\mathcal M, v\models\varphi$ for every $v$, we write $\mathcal M\models\varphi$. A formula is valid if every $\Sigma$-structure $\mathcal M$ satisfies it. We denote the set of valid formulas with \emph{CQC} (Classical Quantified Calculus).
\end{definition}

\begin{definition}
	A $\Sigma$-\emph{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$, called the Kripke \emph{frame}, and an indexed family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$ we have $M_u\subseteq M_w$, $f^{I_w}|_{M_u} = f^{I_u}$ and $R^{I_w}|_{M_u} = R^{I_u}$.\footnote{Here $f|_M$ denotes the restriction of $f$ to $M$}
	The model relation between $\mathcal M_u$, $v$ (mapping into $M_u$) and formulas $\varphi$ is defined as before, except in the cases of implication and $\forall$-quantification, where we set
	\begin{itemize}
		\item $\mathcal M_u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $w, v\not\models\varphi$ or $w, v\models\psi$.
		\item $\mathcal M_u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $w, v[m/a]\models\varphi[a/x]$.
	\end{itemize}
	We write $u, v\models\varphi$ if $\mathcal M_u, v\models \varphi$. $\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. $\varphi$ is valid if it is satisfied by every Kripke structure.
	$\varphi$ is valid for some frame (write $W\models\varphi$) if it is satisfied in every Krike structure with that frame. We denote the set of valid formulas with \emph{IQC} (Intuitionistic Quantified Calculus).
\end{definition}
In addition to propositional tautologies there are now quantified formulas which are classically valid but not intuitionistically, e.g., $\neg\forall x A(x)\to \exists x \neg A(x)$.

@@

\begin{definition}
	For formulas $\varphi$ we define the Skolemization $\varphi^S_Z$ and Herbrandization $\varphi^H_Z$ with respect to a set of variables $Z$ by simultaneous induction:
	\begin{itemize}
		\item $A^S_Z = A^H_Z = A$ for each atomic $A$.
		\item $(\varphi\circ\psi)^X_Z = \varphi^X_Z\circ\psi^X_Z$ for $\circ\in\{\wedge, \vee\}$, $X\in\{S, H\}$.
		\item $(\varphi\to\psi)^S_Z = \varphi^H_Z\to \psi^S_Z$ and $(\varphi\to\psi)^H_Z = \varphi^S_Z\to\psi^H_Z$.
		\item $(\forall x\varphi)^S_Z = \forall x(\varphi[a/x]^S_{Z\cup\{a\}}[x/a])$ where $a$ is a new free variable.\\$(\forall x\varphi)^H_Z = \varphi[s(z_1,\dots,z_n)/x]^H_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$.
		\item $(\exists x\varphi)^S_Z = \varphi[s(z_1,\dots,z_n)/x]^S_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$.\\$(\exists x\varphi)^H_Z = \exists x(\varphi[a/x]^H_{Z\cup\{a\}}[x/a])$ where $a$ is a new free variable.
	\end{itemize}
	Let $$\varphi^S = (\exists x_1\dots\exists x_n \varphi[x_1/a_1\dots x_n/a_n])^S_\emptyset$$ and $$\varphi^H = (\forall x_1\dots\forall x_n \varphi[x_1/a_1\dots x_n/a_n])^H_\emptyset$$ where $a_1,\dots,a_n$ are the free variables occurring in $\varphi$.
\end{definition}

@@

\begin{lemma}\label{lemma:first-order-normal-form}
	For every predicate formula $\varphi$ there exists a nullary relation symol $P$ as well as sets of clauses $\mathcal R,\mathcal X, \mathcal Q$, with $\mathcal R$ containing \emph{flat clauses} of the form
	$$\forall \vec x\left(\bigwedge_i A_i\to \bigvee_jB_j\right),$$
	$\mathcal X$ containing \emph{implication clauses} of the form
	$$\forall \vec x\left((A\to B)\to C\right)$$
	and $\mathcal Q$ containing \emph{quantification clauses} of the form
	$$\forall\vec x\left((\forall y A)\to B\right),$$
	such that $\varphi$ is intuitionistically equivalid to
	$$\left(\bigwedge\mathcal R\wedge\bigwedge \mathcal X\wedge\bigwedge\mathcal Q\right)\to P$$where $A_i, B_i, A, B, C$ are atomic. This size of $\mathcal R, \mathcal X, \mathcal Q$ is linear in the size of $\varphi$. In general this formula will contain new function and relation symbols.
\end{lemma}

@@

\begin{theorem}
	\label{thm:reduction-first-order-short}
	There exists a linear-time procedure that gives for every first-order formula $\varphi$ a formula $\varphi^\#$ such that $\varphi$ is intuitionistically valid if and only if $\varphi^\#$ is classically valid. The size of $\varphi^\#$ is in linear in the size of $\varphi$, however, for each $n$-ary relation symbol in $\varphi$ there is a corresponding $n+1$-ary relation symbol in $\varphi^\#$, and $\varphi$ contains a new binary predicate $E$ as well as a number of new function symbols. Furthermore, there is an effective translation between intuitionistic counter-models of $\varphi$ and classical counter-models of $\varphi^\#$.
\end{theorem}

@@

The most obvious approach to embedding intuitionistic into classical logic is to examine intuitionistic semantics, e.g. Kripke frames, as a classical first order theory. For every propositional variable $A$ consider a unary predicate $A$ of the same name where $A(u)$ expresses that $A$ is true at some world $u$. We can then consider the following naive encoding:

>>>>

\documentclass{easychair}
\usepackage{amsmath, amsfonts, amsthm}
\usepackage{wrapfig}
\usepackage{multicol}
\usepackage[T1]{fontenc}
\usepackage{todonotes}
%
\usepackage{tikz}
\usetikzlibrary{shapes,backgrounds}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}[section]
\theoremstyle{definition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{definition}
\newtheorem{example}[theorem]{Example}
\theoremstyle{definition}
\newtheorem{remark}[theorem]{Remark}

\begin{document}
	%
	\title{Embedding Intuitionistic into Classical Logic}
	%
	%\titlerunning{Abbreviated paper title}
	% If the paper title is too long for the running head, you can set
	% an abbreviated paper title here
	%
	\author{Alexander Pluska \and Florian Zuleger}
	%
	\authorrunning{A. Pluska and F. Zuleger}
	\titlerunning{Embedding Intuitionistic into Classical Logic}
	% First names are abbreviated in the running head.
	% If there are more than two authors, 'et al.' is used.
	%
	\institute{TU Wien, Vienna, Austria}
	%
	\maketitle
\begin{abstract}
The famous double negation translation~\cite{glivenko1929quelques,godel1933intuitionistischen} establishes an embedding of classical into intuitionistic logic.
Curiously, the reverse direction has not been covered in literature.
Utilizing a normal form for intuitionistic logic~\cite{claessen2015sat}, we establish a small model property for intuitionistic propositional logic.
We use this property for a direct encoding of the Kripke semantics into classical propositional logic and quantified boolean formulas.
Next, we transfer the developed techniques to the first order case and provide an embedding of intuitionistic first-order logic into classical first-order-logic.
Our goal here is an encoding that facilitates the use of state-of-the-art provers for classical first-order logic for determining intuitionistic validity.
In an experimental evaluation, we show that our approach can compete with state-of-the-art provers for certain classes of benchmarks, in particular when the intuitionistic content is low.
We further note that our constructions support the transfer of counter-models to validity, which is a desired feature in model checking applications.
\end{abstract}

@@

Constructive mathematics refers to a flavor of mathematics in which the existence of an object can only be established by explicit construction, as opposed to classical mathematics where existence can be shown implicitly, e.g. by assuming non-existence and deriving a contradiction.
The formalism usually associated with constructive mathematics is intuitionistic logic, which essentially differentiates itself from classical logic by the fact that the law of excluded middle $A\vee\neg A$ and the double negation shift $\forall x\neg\neg P(x)\to\neg\neg\forall xP(x)$ are not valid.
Besides philosophical considerations, most prominently advocated by Brouwer~\cite{brouwer1907over} and Bishop~\cite{bishop1967foundations}, there is a particular motivation for studying constructive mathematics from the perspective of computer science in that proofs in intuitionistic logic directly correspond to computer programs --- as expressed in the Curry--Howard correspondence~\cite{howard1980formulae}.

The interest in intuitionistic logic has lead to the development of a number of automated theorem proving systems and a collection of benchmark problems (see e.g. the ILTP library website~\cite{iltp}).
The progress in automated reasoning for intuitionistic logic, however, has been slower than the  impressive advances in solvers for classic logics --- evidenced, e.g., by the CASC~\cite{casc} and SAT~\cite{satc} competitions.
%, e.g., the first-order provers~\cite{kovacs2013first, schulz2002brainiac, korovin2008iprover}
%Comparing benchmarks for classical and intuitionistic automated theorem proving, e.g. TPTP~\cite{casc} and , we see that classical provers currently have a far better success rate. Furthermore all the most popular first-order utilize classical logic.
This difference can partially be explained by fundamental differences between the logics.
First of all, determining intuitionistic validity is computationally harder, e.g., in the propositional case intuitionistic validity is \verb+PSPACE+-complete~\cite{statman1979intuitionistic}, whereas classical validity is \verb+coNP+-complete~\cite{cook1971complexity}.
A further advantage of classical logic is the existence of calculi that are particularly suited for automation, such as superposition~\cite{bachmair2001resolution}, which rely on the existence of convenient normal forms such as CNF, and the duality between validity and satisfiability (i.e., in order to show the validity of a formula it suffices to show the unsatisfiability of the negated formula, which is insufficient in intuitionistic logic).
The first dedicated intuitionistic theorem provers~\cite{mclaughlin2009efficient,tammet1996resolution} used the naïve inverse method, i.e., a direct search for a cut-free proof by applying the rules from some proof calculus inversely, which generally leads to a very complex search. 
More recently, connection-based methods have been applied to various non-classical logics~\cite{otten2005clausal,otten2021nanocop}, including intuitionistic logic.
There have also been some successful attempts to study intuitionistic validity via embedding into higher-order classical logic~\cite{LEO}.
We finally add that, in contrast to intuitionistic provers, a tremendous amount of work has been put into optimizing provers for classical logic.

@@

In this section we fix notation and recall the semantics for classical and intuitionistic logic. Furthermore we recapitulate some results from~\cite{otten2005clausal}.

\subsection{Syntax}

For propositional logic we assume an ambient set of propositional variables. A propositional formula is defined inductively as follows:
\begin{itemize}
	\item The propositional constant $\bot$ is a formula.
	\item Each propositional variable is a formula.
	\item Given formulas $\varphi$ and $\psi$ and a connector $\circ\in\{\wedge, \vee,\to\}$ there is a formula $\varphi\circ\psi$.
\end{itemize}

For predicate logic we assume an ambient signature $\Sigma$, i.e., a set of function and predicate symbols with their respective arities, and sets of free and bound variables. Generally free variables will be denoted will letters at the beginning of the alphabet while bound variables will be denoted with letters at the end of the alphabet. $\nu$ will usually be a placeholder that can be instantiated with free or bound variables. We can define terms $t$ and substitutions $t[\nu/b]$ by simultaneous induction as follows:
\begin{itemize}
	\item Each free variable $a$ is a term and $a[\nu/b] := \begin{cases}
		\nu & \text{if } a = b \\
		a & \text{otherwise}
	\end{cases}$.
	\item For each $n$-ary function symbol $f$ and terms $t_1, \ldots, t_n$ we have that $f(t_1, \ldots, t_n)$ is a term and $f(t_1, \ldots, t_n)[\nu/b] := f(t_1[\nu/b], \ldots, t_n[\nu/b])$.
\end{itemize}
We can then define formulas $\varphi$ and substitutions $\varphi[\nu/b]$ by simultaneous induction as follows:
\begin{itemize}
	\item The constant $\bot$ is a formula and $\bot[\nu/b] := \bot$.
	\item For each $n$-ary predicate symbol $P$ and terms $t_1, \ldots, t_n$ we have that $P(t_1, \ldots, t_n)$ is a formula and $P(t_1,\ldots, t_n)[\nu/b] := P(t_1[\nu/b], \ldots, t_n[\nu/b])$.
	\item Given formulas $\varphi$ and $\psi$ and a connector $\circ\in \{\wedge,\vee,\to\}$ there is a formula $\varphi\circ\psi$ and $(\varphi\circ\psi)[\nu/b] := \varphi[\nu/b]\circ\psi[\nu/b]$.
	\item Given a formula $\varphi$, a free variable $a$, a bound variable $x$ not occurring in $\varphi$ and a quantifier $Q\in\{\exists,\forall\}$ there is a formula $Qx(\varphi[x/a])$ and $Qx(\varphi[x/a])[\nu/b] := Qx(\varphi[x/a][\nu/b])$.
\end{itemize}

@@

\begin{definition}
	Let $\Sigma$ be a signature. A $\Sigma$-structure $\mathcal{M}$ consists of a non-empty set $M$, the \emph{domain} of $\mathcal{M}$, and an \emph{interpretation} $I$ that assigns
	\begin{itemize}
		\item to each $n$-ary function symbol $f\in\Sigma$ a $n$-ary function $f^I: M^n\to M$.
		\item to each $n$-ary predicate symbol $R\in\Sigma$ a $n$-ary predicate $R^I\subseteq M^n$.
	\end{itemize}
	A variable assignment $v$ is a function that assigns to each free variable an element $m\in M$. For each free variable $a$ and $m\in M$ we define $$v[m/a](b) = \begin{cases}
	m, &\text{if $b=a$,}\\
	v(b), &\text{otherwise.}
	\end{cases}$$
	Then terms are interpreted as follows:
	\begin{itemize}
		\item $a^{I, v} = v(a)$ for each free variable $a$.
		\item $f(t_1,\dots,t_n)^{I, v} = f^I(t_1^{I, v},\dots, t_n^{I, v})$ for each $n$-ary function symbol $f\in\Sigma$.
	\end{itemize}
	We define a model relation between pairs $\mathcal M, v$ and formulas $\varphi$ as follows
	\begin{itemize}
		\item $\mathcal M, v\not\models\bot$
		\item $\mathcal M, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I, v},\dots,t_n^{I, v})\in R^I$, $\mathcal M, v\models s = t$ iff $s^{I, v} = t^{I, v}$.
		\item $\mathcal M, v\models \varphi\wedge \psi$ iff $\mathcal M, v\models\varphi$ and $\mathcal M, v\models\psi$
		\item $\mathcal M, v\models \varphi\vee\psi$ iff $\mathcal M, v\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\to\psi$ iff $\mathcal M, v\not\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models\exists x\varphi$ iff there exists $m\in M$ such that $\mathcal M, v[m/a]\models\varphi[a/x]$.
		\item $\mathcal M, v\models\forall x\varphi$ iff for all $m\in M$ we have $\mathcal M, v[m/a]\models\varphi[a/x]$.
	\end{itemize}
	 Here $a$ is a free variable that does not occur in $\varphi$. A $\Sigma$-structure $\mathcal M$ satisfies $\varphi$ if $\mathcal M, v\models\varphi$ for every $v$, we write $\mathcal M\models\varphi$. A formula is valid if every $\Sigma$-structure $\mathcal M$ satisfies it. We denote the set of valid formulas with \emph{CQC} (Classical Quantified Calculus).
\end{definition}

\begin{definition}
	A $\Sigma$-\emph{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$, called the Kripke \emph{frame}, and an indexed family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$ we have $M_u\subseteq M_w$, $f^{I_w}|_{M_u} = f^{I_u}$ and $R^{I_w}|_{M_u} = R^{I_u}$.\footnote{Here $f|_M$ denotes the restriction of $f$ to $M$}
	The model relation between $\mathcal M_u$, $v$ (mapping into $M_u$) and formulas $\varphi$ is defined as before, except in the cases of implication and $\forall$-quantification, where we set
	\begin{itemize}
		\item $\mathcal M_u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $\mathcal M_w, v\not\models\varphi$ or $\mathcal M_w, v\models\psi$.
		\item $\mathcal M_u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $\mathcal M_w, v[m/a]\models\varphi[a/x]$.
	\end{itemize}
	We write $u, v\models\varphi$ if $\mathcal M_u, v\models \varphi$. $\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. $\varphi$ is valid if it is satisfied by every Kripke structure.
	$\varphi$ is valid for some frame (write $W\models\varphi$) if it is satisfied in every Kripke structure with that frame. We denote the set of valid formulas with \emph{IQC} (Intuitionistic Quantified Calculus).
\end{definition}
In addition to propositional tautologies there are now quantified formulas which are classically valid but not intuitionistically, e.g., $\neg\forall x A(x)\to \exists x \neg A(x)$.

@@

\begin{definition}\label{definition:skolemization}
	For formulas $\varphi$ we define the Skolemization $\varphi^S_Z$ and Herbrandization $\varphi^H_Z$ with respect to a set of free variables $Z$ by simultaneous induction:
	\begin{itemize}
		\item $A^S_Z = A^H_Z = A$ for each atomic $A$.
		\item $(\varphi\circ\psi)^X_Z = \varphi^X_Z\circ\psi^X_Z$ for $\circ\in\{\wedge, \vee\}$, $X\in\{S, H\}$.
		\item $(\varphi\to\psi)^S_Z = \varphi^H_Z\to \psi^S_Z$ and $(\varphi\to\psi)^H_Z = \varphi^S_Z\to\psi^H_Z$.
		\item $(\forall x\varphi)^S_Z = \forall x(\varphi[a/x]^S_{Z\cup\{a\}}[x/a])$ where $a$ is a new free variable.\\$(\forall x\varphi)^H_Z = \varphi[s(z_1,\dots,z_n)/x]^H_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$.
		\item $(\exists x\varphi)^S_Z = \varphi[s(z_1,\dots,z_n)/x]^S_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$.\\$(\exists x\varphi)^H_Z = \exists x(\varphi[a/x]^H_{Z\cup\{a\}}[x/a])$ where $a$ is a new free variable.
	\end{itemize}
	Let $$\varphi^S = (\exists x_1\dots\exists x_n \varphi[x_1/a_1\dots x_n/a_n])^S_\emptyset$$ and $$\varphi^H = (\forall x_1\dots\forall x_n \varphi[x_1/a_1\dots x_n/a_n])^H_\emptyset$$ where $a_1,\dots,a_n$ are the free variables occurring in $\varphi$.
\end{definition}

@@

\begin{lemma}\label{lemma:first-order-normal-form}
	For every predicate formula $\varphi$ there exists a nullary predicate symbol $P$ as well as sets of clauses $\mathcal R,\mathcal X, \mathcal Q$, with $\mathcal R$ containing \emph{flat clauses} of the form
	$$\forall \vec x\left(\bigwedge_i A_i\to \bigvee_jB_j\right),$$
	$\mathcal X$ containing \emph{implication clauses} of the form
	$$\forall \vec x\left((A\to B)\to C\right)$$
	and $\mathcal Q$ containing \emph{quantification clauses} of the form
	$$\forall\vec x\left((\forall y A)\to B\right),$$
	such that $\varphi$ is intuitionistically equivalid to
	$$\left(\bigwedge\mathcal R\wedge\bigwedge \mathcal X\wedge\bigwedge\mathcal Q\right)\to P$$where $A_i, B_i, A, B, C$ are atomic. This size of $\mathcal R, \mathcal X, \mathcal Q$ is linear in the size of $\varphi$. In general this formula will contain new function and predicate symbols.
\end{lemma}

@@

\begin{theorem}
	\label{thm:reduction-first-order-short}
	There exists a linear-time procedure that gives for every first-order formula $\varphi$ a formula $\varphi^\#$ such that $\varphi$ is intuitionistically valid if and only if $\varphi^\#$ is classically valid. The size of $\varphi^\#$ is in linear in the size of $\varphi$, however, for each $n$-ary predicate symbol in $\varphi$ there is a corresponding $n+1$-ary predicate symbol in $\varphi^\#$, and $\varphi$ contains a new binary predicate $E$ as well as a number of new function symbols. Furthermore, there is an effective translation between intuitionistic counter-models of $\varphi$ and classical counter-models of $\varphi^\#$.
\end{theorem}

@@

The most obvious approach to embedding intuitionistic into classical logic is to examine intuitionistic semantics, e.g. Kripke frames, as a classical first order theory. For every propositional variable $A$ consider a unary predicate $A$ of the same name where $A(u)$ expresses that $A$ is true at some world $u$. We can then consider the following naïve encoding:

\begin{definition}
	Let $\varphi$ be a propositional formula. Define $\varphi^{\nu}$ inductively:
	\begin{itemize}
		\item $\bot^\nu = \bot$.
		\item $A^{\nu} = A(\nu)$ for every propositional variable $A$.
		\item $(\varphi\circ\psi)^\nu = \varphi^\nu\circ\psi^\nu$ for $\circ\in\{\wedge, \vee\}$.
		\item $(\varphi\to \psi)^\nu = \forall w(\nu\preceq w\to\varphi^{w}\to\psi^{w})$ where $w$ is some new bound variable.
	\end{itemize}
	Let $K(\varphi)$ encode the theory of Kripke structures, i.e.
	$$K(\varphi) = \text{\normalfont PartialOrder}(\preceq)\wedge\forall u\forall w(u\preceq w\to \text{\normalfont Persistent}(u, w))$$
	with e.g.
	\begin{align*}
		\text{\normalfont PartialOrder}(\preceq) =&\:\forall u(u\preceq u)\wedge\forall u\forall w(u\preceq w\to w\preceq u\to u = w)\wedge\\&\:\forall u\forall v\forall w(u\preceq v\to v\preceq w\to u\preceq w)\\
		\text{\normalfont Persistent}(u, w)=&\:\bigwedge \{A(u)\to A(w)\:|\: \text{ $A$ occurs in $\varphi$}\}
	\end{align*}
	Then define
	$$\varphi^{C} = K(\varphi)\to \varphi^{b}$$
	where $b$ is a new free variable.
\end{definition}
